%-------------------------
% Resume in Latex
% Author : Vrinda Gupta
% Website: https://github.com/vrindag
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/vrinda-gupta/}{\Large Vrinda Gupta}} & \textbf{Email} : \href{mailto:vrinda.cse.118@gmail.com}{vrinda.cse.118@gmail.com}\\
  \href{https://www.linkedin.com/in/vrinda-gupta//}{linkedin.com/in/vrinda-gupta} & \textbf{Mobile} : +1-408-717-1652 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Institute of Technology and Management}{Gurgaon, IN}
      {Master of Technology in Computer Science;  GPA: 3.44}{Aug. 2012 -- May. 2014}
    \resumeSubheading
      {Punjab Technical University}{Punjab, IN}
      {Bachelor of Technology in Computer Science;  GPA: 3.5}{Aug. 2008 -- Apr. 2012}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, SQL, Java}
     \hspace{1.5in} 
     \textbf{Platforms}{: MacOS, Linux}\hspace{1\textwidth}
   }
   \item{
     \textbf{Technologies}{: Hive, Hadoop, Presto, Yarn}
          \hspace{0.75in} 
     \textbf{Tools}{: Tableau, Dataswarm}\hspace{1\textwidth}

   }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Accenture, Consultant at Facebook}{Menlo Park, CA}
      {Data Engineer}{Aug 2019 - Present}
      \resumeItemListStart
        \resumeItem{Data Pipelines for Campaign}
        {Designed and implemented various rule-based data pipelines to target a specific audience for market promotions and campaigns, and feed data to required channels like AYMT, TCM, CMS, etc.}
        
        \resumeItem{DB Schema design}{Responsible for gathering requirements and designing scalable data marts for various projects like Longtail Ads Campaign and Boost-up resurrection, which can directly be used to feed the dashboards.}
        
        \resumeItem{Building Metrics}{Data trend analysis and visualization using dashboards to demonstrate the impact of different ad campaigns.}

        \resumeItem{Python Migration}{Migrated more than 100 pipelines from Python 2 to Python 3.}
    
      \resumeItemListEnd

    \resumeSubheading
      {Absolutdata Research and Analytics Ltd}{Gurgaon, IN}
      {Senior Programmer}{Jan 2018 - Nov 2018}
      \resumeItemListStart
        \resumeItem{Conversational chatbot}{Created a pluggable chatbot powered by Google Dialogflow, that could respond to various internal queries related to HR info, Admin info, etc. to improve the knowledge discovery within the company.}
        \resumeItem{Data ingestion pipeline}{Created data ingestion pipeline for an aviation company that ingested realtime data using Kafka, preprocessed the data using spark streaming and then stored it in MongoDB. The data was later used for analysis and visualization purposes.}
        \resumeItem{Walmart data pipeline}{Pre-processed the data received from Walmart and created partition tables that were fed into our ETL tool.}
      \resumeItemListEnd

    \resumeSubheading
      {Absolutdata Research and Analytics Ltd}{Gurgaon, IN}
      {Analyst}{Aug  2016 - Dec 2017}
      \resumeItemListStart
        \resumeItem{Mondelez}{Retrieved and processed data using Hive for Mondelez. The project also involved validation and transformation of the data for visualization. I also worked on the automation of the whole pipeline}
        \resumeItem{Other} {Responsible for drafting technical documentation with detailed design and implementation details.}
      \resumeItemListEnd


\resumeSubheading
      {GyanSha InfoTech}{Gurgaon, IN}
      {Hadoop Developer}{Aug  2014 - Jul 2016}
      \resumeItemListStart
        \resumeItem{Hadoop Instructor}{Gave Hadoop, Hive and Oozie training to internal and external developers}
        \resumeItem{Discovery} {Conducted experiments to compare performance of various NoSQL database on AWS instances.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------------

\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubItem{Performance Comparison of NoSQL Databases using RESTful API calls}
      {(ICSSS 2016, Chennai, IN)}
    \resumeSubItem{3 RFID related publications }
      {\href{http://www.digitalxplore.org/up_proc/pdf/48-1393418802111-116.pdf}{link} (IRF), \href{hhttp://www.ripublication.com/irph/ijict_spl/ijictv4n5spl_15.pdf}{link} (IJICT), 
\href{https://www.academia.edu/7177897/D016172330}{link} (IOSR), 
}
  \resumeSubHeadingListEnd

%-----------HONORS AND AWARDS-----------------

\section{Honors And Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{Employee of the month}{at Absolutdata for work on Mondelez project}
    \resumeSubItem{Innovation award}{for the conversational chatbot project at  Absolutdata.}
    \resumeSubItem{Best Research Paper}{Won the best research paper award in 2016 IEEE International Conference on Smart Structures and Systems.}
      

  \resumeSubHeadingListEnd

%
%-------------------------------------------
\end{document}
